---
title: 'Event Studies'
author: 'Takuma Kinoshita'
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(broom)
library(sf)
library(rgdal)
library(lme4)
library(rstan)
library(brms)
library(bayesplot)
library(scales)

rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
```

## Load Data

    - Filter out non-metropolitan areas to make the price trend closer to parellel.
    - Filter out non-housing usage land to focus people's behavior (not firms behaviour) dasfaf

```{r}
islands <- c('東京大島', '新島', '神津島', '小笠原', '八丈', '東京三宅')
metro_areas <- c("千代田", "中央", "港", "新宿", "文京", "台東", "墨田",
                 "江東", "品川", "目黒", "大田", "世田谷", "渋谷", "中野",
                 "杉並", "豊島", "北", "荒川", "板橋", "練馬", "足立", "葛飾", "江戸川")

data <- read_sf('../data/input/prices_and_maps_tokyo.geojson', as_tibble = TRUE)

# filtering
data <- data %>% 
    filter(duplicate_no == 0) %>%  # only first publish of map
    filter((!city %in% islands)) %>%  # remove islands
    filter(city %in% metro_areas)  # only metropolitan
    # filter(grepl("住宅", usage))  # only housing usage
    
# give id to each location
data <- data %>% 
    mutate(land_id_full = paste0(city_id, land_category, land_id))

data
plot(data, max.plot = 1)
```


# one year & one price per row

```{r}
# make vector of "price_????"
price_cols = c()
i = 1
for (col in names(data)) {
    if (grepl("price", col, fixed = TRUE)) {
        price_cols <- append(price_cols, col)
        i <- i + 1
    }
}

# wide to long
long <- data %>% 
    gather("price_year", "price", all_of(price_cols)) %>%
    mutate(price = as.numeric(price)) %>% 
    mutate(price_year = str_replace_all(price_year, pattern = "price_", replacement = "")) %>%  # remove prefix of price_year
    filter(price != 0) %>%  # only rows with price
    mutate(price_date = as.POSIXct(paste(price_year, 1, 1, sep = "-")))  # convert year from string to POSIX

long[c("land_id_full", "price_year", "price_date", "price")]
```

# create some features

    - create time difference variable (time_lapse = land price evaluated date - hazard map published date)
    - create inundation flag (is_depth). If there is expected inundation 1, otherwise 0

```{r}
# time lapse
long <- long %>%
    mutate(time_lapse = price_date - map_date) %>%  # time lapse days
    mutate(time_lapse_year = ceiling(as.numeric(time_lapse) / 365)) %>% 
    mutate(time_lapse_year = replace_na(time_lapse_year, -999))# time lapse years

# is_depth
long <- long %>% 
    mutate(is_depth = !is.na(water_depth_scaled))

table(long$is_depth)
long[c("land_id_full", "price_date", "map_date", "time_lapse", "time_lapse_year")]
```

# Explanatory data analysis

    - Raw land price follows heavy-tailed distribution
    - I applied logarithmic transformation to make it almost gaussian

```{r}
# distribution of price
plot_price <- function(data, x, title) {
    ggplot(data, aes(x = x)) +
        geom_histogram(position = "identity", alpha = 0.9, bins = 200) +
        xlab("Land Price [JPY]") +
        scale_y_continuous(limits = c(0, 2500)) +
        theme_bw()
}
```

```{r}
long <- long %>% mutate(price_log = log10(price))  # log of price
long_2019 = long[long$price_year == 2019,]

summary(long[c("price", "price_log")])

# without log
wo_log <- plot_price(long, long$price) +
  scale_x_continuous(breaks = seq(0, 1 * 10 ** 7, by = 2 * 10 ** 6), limits = c(0, 1 * 10 ** 7))

# with log
w_log <- plot_price(long, long$price, "log price all years") +
  scale_x_log10(breaks = 10 ** (0:8), limits = c(1, 10 ** 8)) +
  annotation_logticks(side = "b")

dist_fig <- gridExtra::grid.arrange(wo_log, w_log)
ggsave(dist_fig, device = "png", file = "../figures/price_dist.png")
```

    - log price follows different distribution depending on city_id and year
    - Adding random effect or interaction term of city_id and year is reasonable

```{r}
district_fig <- ggplot(long, aes(x = factor(city), y = price)) +
    geom_boxplot() +
    theme_gray(base_family = "HiraKakuPro-W3") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    scale_y_log10(breaks = 10 ** (0:8), limits = c(10 ** 5, 10 ** 8)) +
    xlab("District in Tokyo") + ylab("Land Price [JPY]")
ggsave(district_fig, filename = "../figures/district_dist.png", width = 10, height = 4)

year_fig <- ggplot(long, aes(x = factor(price_year), y = price)) +
    geom_boxplot() +
    scale_y_log10(breaks = 10 ** (0:8), limits = c(10 ** 5, 10 ** 8)) +
    xlab("Year") + ylab("Land Price [JPY]") + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave(year_fig, filename = "../figures/year_dist.png", width = 10, height = 4)

ggplot(long, aes(x = factor(time_lapse_year), y = price_log)) +
    geom_boxplot() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

    - Publications of hazard maps were between 2002 and 2010 
    - Most of the points are covered by the publication at 2005/07/08

```{r}
table(long$map_date)
```

    - The mean log price shows parellel trend between area with inundation and one without inundation.
    - The size of the difference became larger between (1) 1987 ~ 1992 and (2) 1999 ~ 2006
    - (1) is probably caused by bubble economy. Non-inundation area is historically richer area which got more investment
    - (2) is probably caused by development of many skyscrapers as an economic boosting measure, which mainly happened in non-inundation area

```{r}
mean_sd = long %>% 
    group_by(price_year, is_depth) %>% 
    summarise(mean = mean(price_log), sd = sd(price_log))

ggplot(mean_sd, aes(x = price_year, y = mean, color = is_depth, group = is_depth)) +
    geom_errorbar(aes(ymin = mean - sd, ymax = mean + sd)) +
    geom_line() + geom_point() +
    theme_gray(base_family = "HiraKakuPro-W3") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r fig.width=7, fig.height=4}
mean_sd = long %>% 
    group_by(price_year, is_depth, city) %>% 
    summarise(mean = mean(price_log), sd = sd(price_log))

ggplot(mean_sd, aes(x = price_year, y = mean, color = is_depth, group = is_depth)) +
    geom_errorbar(aes(ymin = mean - sd, ymax = mean + sd)) +
    geom_line() + geom_point() +
    theme_gray(base_family = "HiraKakuPro-W3") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    facet_wrap(~city)
```

```{r}
ggplot(data = long, mapping = aes(x = as.numeric(time_lapse), y = price_log, color = factor(map_date))) +
    geom_point(size = 0.5)
```


```{r}
long_2019
```


## Linear Model

```{r}
model_lm <- lm(data = long, formula = price_log ~ factor(time_lapse_year))
summary(model_lm)
par(mfrow = c(2, 2))
plot(model_lm)

coef_tb <- model_lm %>% 
    tidy(conf.int = TRUE) %>% 
    filter(term != '(Intercept)') %>% 
    mutate(term = gsub(term, pattern = 'factor\\(time_lapse_year\\)', replacement = '')) %>% 
    mutate(term = as.integer(term))
coef_tb

ggplot(data = coef_tb) +
    geom_pointrange(aes(x = term, y = estimate, ymin = conf.low, ymax = conf.high))
```

## Linear Mixed Model (Only random intercept)


```{r}
model_lmm <- lmer(data = long, formula = price_log ~ factor(time_lapse_year) + (1 | price_year) + (1 | city_id))
summary(model_lmm)
plot(model_lmm)
qqnorm(resid(model_lmm))
qqline(resid(model_lmm))

coef_tb <- model_lmm %>% 
    tidy(conf.int = TRUE) %>% 
    filter(group == 'fixed') %>%
    filter(term != '(Intercept)') %>%
    mutate(term = gsub(term, pattern = 'factor\\(time_lapse_year\\)', replacement = '')) %>% 
    mutate(term = as.integer(term))
coef_tb

ggplot(data = coef_tb) +
    geom_pointrange(aes(x = term, y = estimate, ymin = conf.low, ymax = conf.high)) +
    xlim(-5, 10) +
    xlab("Land price evaluation year - Hazard map publication year") + ylab("Mean land price difference(Treated - Control)")
```



